### 2010-06-28 trunk/paper/IIWAS2010/content/introduction.tex
changes to introduction

[[Need a paragraph for wiki page categorization and ontology construction]]
In this paper, we propose an automatic web page categorization or 
classification and recommendation using a machine learning technique, topic modeling.
In addition, we also describes how we can use the categorized pages for realm-ontology 
creation.

This paper starts by discussing state-of-the-art systems in the area of
question answering and ontology generation. The system
architecture section explains the Morpheus system and its implementations
details. In the results section, we describe current results and its
interpretations. Finally, we conclude the paper by describing the global impacts
of our approaches in QA systems, WWW page categorization, and ontology
generators.

>>>>

This paper starts by discussing state-of-the-art systems in the area of
question answering and ontology generation. The system
architecture section explains the Morpheus system and its implementations
details. In the results section, we describe current results and its
interpretations. Finally, we conclude the paper by describing the global impacts
of our approaches in QA systems.
